Process Heritability Data

### 2021-06-25 R/02-process-herit.Rmd
convert heritability script to Rmd

```{r initialize_packages, message=FALSE}
library(tidyverse)
```

@@

```{r process_herit_data}
# Pull out the selected parental jars
selected <- 
  fluxes[paste0(fluxes$passage, fluxes$jar) %in% paste0(selected_jars$passage, selected_jars$jar), ] %>%
  select(treat, estimate, passage)

# Pull out all parental jars
parental <-
  fluxes %>% 
  select(passage, treat, estimate)

# Pull out all offspring jars
# The `passage - 1` function sets the value of generation `n + 1` 
# as the "offspring" value for generation `n`. 
offspring <- 
  fluxes %>%
  select(treat, estimate, passage) %>% 
  filter(passage != 1) %>% 
  mutate(passage = passage - 1)

# Calculate means within each generation for all parental jars,
# all offspring jars, and all selected parental jars
parental_mean <-
  parental %>% 
  group_by(passage, treat) %>% 
  summarize(parental = mean(estimate), .groups = "drop")

offspring_mean <-
  offspring %>% 
  group_by(passage, treat) %>% 
  summarize(offspring = mean(estimate), .groups = "drop")

selected_mean <-
  selected %>% 
  group_by(passage, treat) %>% 
  summarize(selected = mean(estimate), .groups = "drop")

# Combine all parent/offspring data into one data frame
heritability <- 
  parental_mean %>% 
  left_join(offspring_mean, by = c("passage", "treat")) %>% 
  left_join(selected_mean, by = c("passage", "treat")) %>% 
  #filter(treat == "p") %>% 
  filter(passage != 5) %>% # Remove passage 5, which has no offspring,
  # because it's the last generation
  ungroup()

write_tsv(heritability, paste0(der_dir, 'heritability.tsv'))
```

>>>>

```{r initialize_packages, message=FALSE}
library(tidyverse)
library(knitr)
```

@@

```{r process_herit_data}
# Pull out the selected parental jars
selected <- 
  fluxes %>% 
  filter(selected) %>% 
  select(passage, treat, log_ch4)

# Pull out all parental jars
parental <-
  fluxes %>% 
  select(passage, treat, log_ch4)

# Pull out all offspring jars
# The `passage - 1` function sets the value of generation `n + 1` 
# as the "offspring" value for generation `n`. 
offspring <- 
  fluxes %>%
  select(treat, log_ch4, passage) %>% 
  filter(passage != 1) %>% 
  mutate(passage = passage - 1)

# Calculate means within each generation for all parental jars,
# all offspring jars, and all selected parental jars
parental_mean <-
  parental %>% 
  group_by(passage, treat) %>% 
  summarize(parental = mean(log_ch4), .groups = "drop")

offspring_mean <-
  offspring %>% 
  group_by(passage, treat) %>% 
  summarize(offspring = mean(log_ch4), .groups = "drop")

selected_mean <-
  selected %>% 
  group_by(passage, treat) %>% 
  summarize(selected = mean(log_ch4), .groups = "drop")

# Combine all parent/offspring data into one data frame
heritability <- 
  parental_mean %>% 
  left_join(offspring_mean, by = c("passage", "treat")) %>% 
  left_join(selected_mean, by = c("passage", "treat")) %>% 
  #filter(treat == "p") %>% 
  filter(passage != 5) %>% # Remove passage 5, which has no offspring,
  # because it's the last generation
  ungroup()
```

```{r print_data}
kable(heritability)
```

```{r export_data}
write_tsv(heritability, paste0(der_dir, 'heritability.tsv'))
```
